Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/contributions.tex
Updated the contributions to be better.

\subsection*{Part II: Most Significant Contributions to Research \& Development}
%\textit{Describe your role in research, clarify your contribution, provide
%    details on significance of tech report, indicate collaborations, discuss
%relevance to engineering practice (if appropriate)}
``The R\'{e}nyi Deterministic Information Bottleneck and Geometric
Clustering" is a technical report about a new information-theoretic tool for
clustering datapoints.
I contributed to this report by producing all the theoretical and simulation
results, though I could not have done this without the abundant advice of my
supervisor, Fady Alajaji. 
I also wrote the report in its entirety.
This report was used by two undergraduate groups at Queen's University for their
honours theses in 2019, and it motivated further research [1].

@@

    \item \textbf{Radar Developer, University of Toronto, 2018}.
        In the group project for a graduate course, I worked with three other
        students to write software which reads data from a radar device.
        This project taught me several engineering skills.
        First, I improved my project management skills by keeping our group
        meetings organized, and by separating the tasks in such a way
        that everyone was learning something from the project.
        I learned to read hardware documentation and to wire a device from
        schematics.
        I wrote networking code in Python to interface with the
        device, and validatet the hardware's capabilities for myself by
        creating appropriate testing environments. 
        All these skills will be beneficial for my PhD research when I build a
        robot.

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}.
        For my undergraduate thesis, I worked with my peers to find an
        application for existing theoretical results. 
        During this project I also learned to perform a basic literature review,
        and to manage deadlines with a supervisor.
        In terms of engineering skills, I learned to write reports in LaTeX
        and my thesis group worked together on code optimization: we learned to
        convert equations into matrix form to take advantage of hardware
        optimization; we parallelized our code so our algorithm would run faster
        through multithreading; we ported MATLAB code to C++ to achieve even
        faster results; and we created a GUI so we could test our code quickly
        and easily.

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career, as it is what drove
        me to pursue research in robotics.
        Working at Neptec exposed me to several areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        I loved this project, and I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        I also learned to work on large software projects, where multiple people work
        together on the same topic; 
        and I became extremely proficient at software development, a skill which
        has served me well in my research experiments on physical robots.

@@

Over the course of my career, I have enjoyed several extracurricular roles which
developed my communication, interpersonal, and leadership skills.
What follows is a brief description of some of these roles.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund, which is the events
    committee for Massey College (an interdisciplinary college at the University
    of Toronto).
    I have already organized 13 events for members of the college, and will
    continue to organize biweekly events throughout the year.
    This role has taught me the logistics and leadership skills required to
    manage large events for 150 people.
    I have also learned to make events accessible to everyone by asking
    questions so I can understand the needs of all attendees.

@@

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team, 2017 -- 2018}. 
    In this role, I taught C++ and information theory to the team’s software
    developers. I learned project management skills by organizing
    the satellite codebase and handling code reviews, and I took on a supportive
    and mentorship role for my peers rather than writing software myself.

\item \textbf{Head Programming Mentor, FIRST Team 2809, 2013 -- 2015}. 
    I mentored high school students in Object Oriented programming for robotics
    software. Together we programmed a robot in under 6 weeks and placed 3rd at
    the Ontario provincial competition in 2014.
    In this role I learned to lead my students by giving them agency over the
    project, and to communicate with people from all over the world in
    high-stress situations.

>>>>

\subsection*{Part II: Most Significant Contributions to Research \& Development}
%\textit{Describe your role in research, clarify your contribution, provide
%    details on significance of tech report, indicate collaborations, discuss
%relevance to engineering practice (if appropriate)}
``The R\'{e}nyi Deterministic Information Bottleneck and Geometric
Clustering" is a technical report about a new information-theoretic tool for
clustering datapoints.
I contributed to this report by producing all the theoretical and simulation
results, though I received an abundance of advice from my supervisor, Fady
Alajaji. 
I also wrote the report in its entirety.
This report was used by two undergraduate groups at Queen's University for their
honours theses in 2019, and it motivated further research [1].

@@

    \item \textbf{Radar Developer, University of Toronto, 2018}.
        In the group project for a graduate course, I worked with three other
        students to write software which reads data from a radar device.
        This project taught me several engineering skills.
        First, I improved my project management skills by keeping our group
        meetings organized, and by separating the tasks in such a way
        that everyone was learning something from the project.
        I learned to read hardware documentation and to wire a device from
        schematics.
        I wrote networking code in Python to interface with the
        device, and validated the hardware's capabilities for myself by
        creating appropriate test environments. 
        All these skills will be beneficial for my PhD research when I build a
        robotic monkey.

    \item \textbf{Undergraduate Thesis, Queen's University, 2017 -- 2018}.
        For my undergraduate thesis, I worked with my peers to design an image
        filtering algorithm by applying theoretical results from information theory.
        During this project I learned to perform a basic literature review,
        and to manage deadlines with a supervisor.
        I also learned to write reports in LaTeX,
        and my thesis group worked together on code optimization: we learned to
        convert equations into matrix form to take advantage of hardware
        optimization; we parallelized our code so our algorithm would run faster
        through multithreading; we ported MATLAB code to C++ to achieve even
        faster results; and we created a GUI so we could test our code quickly
        and easily.

    \item \textbf{Software Developer, Neptec Technologies Corp., 2016 -- 2017}.
        My experience at Neptec was integral to my career because it convinced
        me to pursue research in robotics.
        Working at Neptec exposed me to many areas of electrical and computer
        engineering.
        I worked on several embedded software projects, my favourite of which
        was a control systems project.
        After completing this project, I decided to do a master's (and a PhD) so I
        could learn as much about control as possible.
        At Neptec I also learned to work on large software projects, where multiple people work
        together on the same code; 
        and I became extremely proficient at software development, a skill which
        has served me well in my research experiments on physical robots.

@@

Over the course of my career, I have enjoyed several extracurricular
roles which developed my communication, interpersonal, and leadership skills.
Here is a brief description of some of these roles.
\begin{itemize}
\item \textbf{Lionel Massey Fund Co-chair, Massey College, September 2021 -- Present}.
    I am one of six co-chairs for the Lionel Massey Fund, which is the events
    committee for Massey College (an interdisciplinary college at the University
    of Toronto).
    I have already organized 13 events for members of the college, and will
    continue to organize events throughout the year.
    This role has taught me the logistics and leadership skills required to
    manage large events for up to 60 people.
    I have also learned to make events accessible to everyone, and to
    communicate with attendees so I can meet their needs.

@@

\item \textbf{Science Payload Designer, Queen’s University Satellite Design
    Team (QSAT), 2017 -- 2018}. 
    I took on a mentorship role at QSAT, where I taught C++, Git, and information
    theory to the team’s software developers. I helped them organize
    the satellite codebase, managed all code reviews, and provided advice for my
    peers rather than writing software myself.

\item \textbf{Head Programming Mentor, FRC Team 2809, 2013 -- 2015}. 
    In this role, I mentored high school students in Object Oriented programming
    for robotics software. I taught students to program a robot in under 6
    weeks, which earned us 3rd place at the Ontario provincial competition in
    2014.
    In this role I learned to lead my students by giving them agency over the
    project, and to communicate with people from all over the world in
    high-stress situations.
